---
title: "Cue interactions 03-2022 (Markdown)"
author: "Sarah"
date: '2023-03-28'
output: html_document


# Pilot study March 2022 

loading packages 

```{r}
library(dplyr)
library(Matrix)
library(lme4)
library(ggeffects)
library(ggplot2)
```


### loading and cleaning data

larvae were checked for settlement at 10, 20, and 30 hours. However, data points from from 10, 20 were not used in this analysis and are removed here.  

```{r}
setwd("~/GitHub/Conspecific-Predator-Settlement-Cue")
data <- read.csv2(file="Experiment March 2022.csv", sep=",")
data <- select(data, -settled_10hrs, -unattached_10hrs, -settled_20hrs, -unattached_20hrs)
colnames(data)[5] <- 'Settled'
colnames(data)[6] <- 'Unattached'
data$Larvae.batch <- as.factor(data$Larvae.batch)
data$Larvae.age <- as.factor(data$Larvae.age)
```

### Calculate response variable from input data

```{r}
mult_s <- rep(1:nrow(data), data[, 'Settled'])
mult_u <- rep(1:nrow(data), data[, 'Unattached'])
data_s <- data[mult_s,]
data_s[, 'Settled'] <- 1
data_s <- data_s[, !(names(data_s) %in% c('Unattached'))]
data_u <- data[mult_u,]
data_u[, 'Unattached'] <- 0
data_u <- data_u[, !(names(data_u) %in% c('Settled'))]
colnames(data_u)[5] <- 'Settled'
data <- rbind(data_s, data_u)
```


### Adding binary predictor values

```{r}
data['Shell'] <- data['Cue']
data['conspecific_cue'] <- data['Cue']
data['predator_cue'] <- data['Cue']
data$Shell <- ifelse(grepl("Conspecific shell", data$Shell), TRUE, FALSE)
data$conspecific_cue <- ifelse(grepl("conspecific cue", data$conspecific_cue), TRUE, FALSE)
data$predator_cue <- ifelse(grepl("predator cue", data$predator_cue), TRUE, FALSE)
data$Shell <-sub("TRUE", "untreated", data$Shell)
data$Shell <-sub("FALSE", "sterilized", data$Shell)
data$predator_cue <-sub("TRUE", "present", data$predator_cue)
data$predator_cue <-sub("FALSE", "absent", data$predator_cue)
data$conspecific_cue <-sub("TRUE", "present", data$conspecific_cue)
data$conspecific_cue <-sub("FALSE", "absent", data$conspecific_cue)
```

### Making the model 


```{r}
model <- glmer(Settled ~conspecific_cue * predator_cue + (1| Larvae.age) + (1| Larvae.batch) + (1 | Crab), data = data, family = binomial)
summary(model)
```

### plots
```{r}
m <- ggpredict(model, terms = c("conspecific_cue", "predator_cue"))
plot(m) +
  labs(x = 'Conspecific Cue', 
       y= 'Larvae Settled (%)',
       title = "") +
  guides(color = guide_legend(title = "Predator Cue")) +
  scale_color_manual(breaks = c("absent", "present")
                     , labels= c("Absent", "Present"),
                     values = c("dodgerblue3", "orangered4")) +
  scale_y_continuous(labels= function(x) paste0(x*100), limits = c(0,1))
```



